save

### 2024-03-09 msu-masters.qmd
updated website

---

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Box with Rounded Edges</title>
<style>
  .container {
    width: 400px;
    height: auto; /* Set container height */
    border: 0.5px solid #ccc; /* Light grey color */
    border-radius: 8px; /* Less rounded edges */
    overflow: hidden; /* Hide overflow content */
    position: relative;
    display: inline-block;
    transition: box-shadow 0.15s ease; /* Transition for box-shadow */
    box-shadow: 0 2px 5px rgba(0, 0, 0, 0.1); /* Slight shadow by default */
    text-align: center; /* Center content horizontally */
    text-decoration: none; /* Remove underline */
    margin-right: 20px; /* Add margin to create space between boxes */
  }

  .container:last-child {
    margin-right: 0; /* Remove margin from the last box */
  }

@@

  .content {
    width: 100%;
    height: 100%;
    padding: 20px;
    box-sizing: border-box;
  }

  .content img {
    width: 50%;
    height: auto;
    display: block;
    margin: 0 auto; /* Center the image horizontally */
    object-fit: cover; /* Crop the image to cover container */
  }

  .text {
    margin-top: 10px;
    text-align: center; /* Center text within the box */
    text-decoration: none;
  }

  .text h1 {
    font-size: 24px; /* Larger text size */
    margin-top: 1px;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
  }
</style>
</head>
<body>
  <a href="wss.qmd" class="container">
    <div class="content">
      <img src="img/msu-masters/wss.JPG" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="locoweed-report.qmd" class="container">
    <div class="content">
      <img src="img/msu-masters/loco-bee2.jpg" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
</body>
</html>

>>>>

---
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Box with Rounded Edges</title>
<style>
  body {
    margin: 0; /* Remove default margin */
    padding: 0; /* Remove default padding */
  }

  .container {
    width: calc(100% - 20px); /* Adjusted width to fit the screen and account for margins */
    max-width: 600px; /* Limiting maximum width */
    height: auto; /* Set container height */
    border: 0.5px solid #ccc; /* Light grey color */
    border-radius: 8px; /* Less rounded edges */
    overflow: hidden; /* Hide overflow content */
    margin-bottom: 20px; /* Add margin to create space between rows */
    margin-right: auto; /* Push containers to the left */
    margin-left: 10px; /* Adjust margin between the left side of the screen */
    display: flex; /* Use flexbox for layout */
    align-items: center; /* Center items vertically */
    text-decoration: none; /* Remove underline */
  }

  .container:last-child {
    margin-bottom: 0; /* Remove margin from the last box */
  }

@@

  .image-container {
    padding: 20px;
    box-sizing: border-box;
  }

  .image-container img {
    width: 80px; /* Adjusted width for smaller image */
    height: auto;
    display: block;
    border-radius: 8px; /* Rounded corners for image */
  }

  .content {
    padding: 20px;
    box-sizing: border-box;
    flex: 1; /* Take remaining space */
  }

  .text h1 {
    font-size: 18px; /* Adjusted text size */
    margin-top: 0;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
    text-align: justify; /* Align text */
  }

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="wss.qmd" class="container">
    <div class="image-container">
      <img src="img/msu-masters/oviposition.JPG" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="locoweed-report.qmd" class="container">
    <div class="image-container">
      <img src="img/msu-masters/loco-bee2.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
  <a href="toadflax_report.qmd" class="container">
    <div class="image-container">
      <img src="img/msu-masters/toadflax.jpeg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Toadflax</h1>
        <p></p>
      </div>
    </div>
  </a>
</body>
</html>

### 2024-03-09 projects.qmd
updated website

---
title: "Projects"
editor_options: 
  chunk_output_type: console
---
::: {style="display: flex;"}

<figure style="margin-right: 20px; display: flex; flex-direction: column; align-items: center;">
  <a href="msu-masters.qmd">
    <img src="img/msu-logo.jpg" alt="Montana State University" width="200" height="200">
  </a>
  <figcaption style="text-align: center;">Montana State University</figcaption>
</figure>

<figure style="margin-right: 20px; display: flex; flex-direction: column; align-items: center;">
  <a href="bballref.qmd">
    <img src="img/bballref-logo.jpeg" alt="Basketball Reference Tool" width="200" height="200">
  </a>
  <figcaption style="text-align: center;">Basketball Reference Tool</figcaption>
</figure>

:::

>>>>

---
title: "Projects"
editor_options: 
  chunk_output_type: console
---

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Box with Rounded Edges</title>
<style>
  body {
    margin: 0; /* Remove default margin */
    padding: 0; /* Remove default padding */
  }

  .container {
    width: calc(100% - 20px); /* Adjusted width to fit the screen and account for margins */
    max-width: 600px; /* Limiting maximum width */
    height: auto; /* Set container height */
    border: 0.5px solid #ccc; /* Light grey color */
    border-radius: 8px; /* Less rounded edges */
    overflow: hidden; /* Hide overflow content */
    margin-bottom: 20px; /* Add margin to create space between rows */
    margin-right: auto; /* Push containers to the left */
    margin-left: 10px; /* Adjust margin between the left side of the screen */
    display: flex; /* Use flexbox for layout */
    align-items: center; /* Center items vertically */
    text-decoration: none; /* Remove underline */
  }

  .container:last-child {
    margin-bottom: 0; /* Remove margin from the last box */
  }

  .container:hover {
    box-shadow: 0 10px 20px rgba(0, 0, 0, 0.1); /* Increased shadow on hover */
  }

  .image-container {
    padding: 20px;
    box-sizing: border-box;
  }

  .image-container img {
    width: 80px; /* Adjusted width for smaller image */
    height: auto;
    display: block;
    border-radius: 8px; /* Rounded corners for image */
  }

  .content {
    padding: 20px;
    box-sizing: border-box;
    flex: 1; /* Take remaining space */
  }

  .text h1 {
    font-size: 18px; /* Adjusted text size */
    margin-top: 0;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
    text-align: justify; /* Align text */
  }

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="msu-masters.qmd" class="container">
    <div class="image-container">
      <img src="img/projects-logos/msu-logo.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Montana State University Master's</h1>
        <p>Co-advised by Dr. David Weaver and Dr. Tracy Sterling.</p>
      </div>
    </div>
  </a>
  <a href="bballref.qmd" class="container">
    <div class="image-container">
      <img src="img/projects-logos/bballref-logo-circle.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>NBA Roster Analysis Tool</h1>
        <p></p>
      </div>
    </div>
  </a>
</body>
</html>

```

### 2024-03-09 save.qmd
updated commit for today
3/8 first commit
updated website

---
title: "save"
---

@@

>>>>

---
title: "save"
editor_options: 
  chunk_output_type: console
---

@@

# how to see what the default colors are in R
```{r}
library(scales)

for(i in 1:6){
  print(hue_pal()(i))
}
hue_pal()(4)
show_col(hue_pal()(6))

# menu grid of boxes for selection

```{=html}
<!-- <!DOCTYPE html> -->
<!-- <html lang="en"> -->
<!-- <head> -->
<!-- <meta charset="UTF-8"> -->
<!-- <meta name="viewport" content="width=device-width, initial-scale=1.0"> -->
<!-- <title>Box with Rounded Edges</title> -->
<!-- <style> -->
<!--   .container { -->
<!--     width: 1000px; -->
<!--     height: auto; /* Set container height */ -->
<!--     border: 0.5px solid #ccc; /* Light grey color */ -->
<!--     border-radius: 8px; /* Less rounded edges */ -->
<!--     overflow: hidden; /* Hide overflow content */ -->
<!--     position: relative; -->
<!--     display: inline-block; -->
<!--     transition: box-shadow 0.15s ease; /* Transition for box-shadow */ -->
<!--     box-shadow: 0 2px 5px rgba(0, 0, 0, 0.1); /* Slight shadow by default */ -->
<!--     text-align: center; /* Center content horizontally */ -->
<!--     text-decoration: none; /* Remove underline */ -->
<!--     margin-right: 20px; /* Add margin to create space between boxes */ -->
<!--   } -->

<!--   .container:last-child { -->
<!--     margin-right: 0; /* Remove margin from the last box */ -->
<!--   } -->

<!--   .container:hover { -->
<!--     box-shadow: 0 10px 20px rgba(0, 0, 0, 0.1); /* Increased shadow on hover */ -->
<!--   } -->

<!--   .content { -->
<!--     width: 100%; -->
<!--     height: 100%; -->
<!--     padding: 20px; -->
<!--     box-sizing: border-box; -->
<!--   } -->

<!--   .content img { -->
<!--     width: 50%; -->
<!--     height: auto; -->
<!--     display: block; -->
<!--     margin: 0 auto; /* Center the image horizontally */ -->
<!--     object-fit: cover; /* Crop the image to cover container */ -->
<!--   } -->

<!--   .text { -->
<!--     margin-top: 10px; -->
<!--     text-align: center; /* Center text within the box */ -->
<!--     text-decoration: none; -->
<!--   } -->

<!--   .text h1 { -->
<!--     font-size: 24px; /* Larger text size */ -->
<!--     margin-top: 1px; -->
<!--     margin-bottom: 5px; /* Adjust margin between large and small text */ -->
<!--     color: black; -->
<!--   } -->
<!--   .text h1:hover { -->
<!--     color: #2068DC; /* Change text color to blue on hover */ -->
<!--   } -->

<!--   .text p { -->
<!--     font-size: 14px; -->
<!--     margin-top: 5px; -->
<!--     color: #666; -->
<!--   } -->
<!-- </style> -->
<!-- </head> -->
<!-- <body> -->
<!--   <a href="wss.qmd" class="container"> -->
<!--     <div class="content"> -->
<!--       <img src="img/msu-masters/wss.JPG" alt="Image"> <!-- Center the image within the box --> 
<!--       <div class="text"> -->
<!--         <h1>Wheat Stem Sawfly</h1> -->
<!--         <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p> -->
<!--       </div> -->
<!--     </div> -->
<!--   </a> -->
<!--   <a href="locoweed-report.qmd" class="container"> -->
<!--     <div class="content"> -->
<!--       <img src="img/msu-masters/loco-bee2.jpg" alt="Image"> <!-- Center the image within the box -->
<!--       <div class="text"> -->
<!--         <h1>Locoweed Volatiles</h1> -->
<!--         <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p> -->
<!--       </div> -->
<!--     </div> -->
<!--   </a> -->
<!--   <a href="toadflax_report.qmd" class="container"> -->
<!--     <div class="content"> -->
<!--       <img src="img/msu-masters/toadflax.jpeg" alt="Image"> <!-- Center the image within the box --> 
<!--       <div class="text"> -->
<!--         <h1>Toadflax</h1> -->
<!--         <p></p> -->
<!--       </div> -->
<!--     </div> -->
<!--   </a> -->
<!-- </body> -->
<!-- </html> -->
